---
title: "Hurricane Harvey in America "
author: xueting tao
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#project description

A major disaster is currently underway with [hurricane Harvey](https://en.wikipedia.org/wiki/Hurricane_Harvey). Use social media data (Twitter, Instagram, Reddit etc.) to identify times and areas that are hardest hit from the hurricane 

#basic data source

* [twitter](https://twitter.com/)
* [instagrame](https://www.instagram.com/?hl=en)
* [reddit](https://www.reddit.com/search?q=hurricane+harvey)

#main place extracted:




When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
